Manuscript drafts

### 2020-03-03 manuscript/drafts/manuscript.Rmd
update introduction

\newpage
# Introduction
SR are booming
ML tools as well
Literature reviews 
machine learning algorithms have been proposed to reduce workload in abstract screening.

@@

[@PRISMA-PGroup2015]

What must be the objective of our tool?

@@

@@

A simulation consists of the following elements:
we have a model $M$ with (hyper)parameters $h$, performing an automated systematic review on SR dataset $d$. 
The model starts with 5 inclusions and 5 exclusions, randomly selected. The simulation is repeated for 10 trials $t$.

for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

@@

>>>>

\newpage
# Introduction
Systematic Reviews (SR's) are booming - but they are a lot of work
Various machien learning tools have been proposed to reduce workload in abstract screening.

@@

A SR can be divided into phases. 
Everything starts with a **systematic search**, leading to
then citation screening is performed, then full-text screening
[@PRISMA-PGroup2015]

What must be the objective of our tool?:
It is the tedious task citation screening part where loads of time can be saved.

models are designed in a 'realistic' way (you have some inclusions)

@@

## Background
[@Yu2018a, @Yu2019] simulated 32 svm classifiers, on software engineering.

In terms of Yu et al, we adopt .CT.

Our extensions is that we try different classifiers, on more datasets.

@@

A simulation is of one model on one dataset. 
we have a model $M$ using a classifier $c$ with (hyper)parameters $h$, performing an automated systematic review on SR dataset $d$. 
The model starts with 5 inclusions and 5 exclusions, randomly selected. The simulation is repeated for 10 trials $t$. 
We use 5 inclusions and exclusions as we assume the researcher has some prior knowledge on this. 
for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

@@

assumptions

 - decisions of the original SR are **ground truth** (benchmark) (oracle)

 - binary classifications: relevant/irrelevant
